The effects of uncertain context inference on motor adaptation

### 2022-05-11 adaptation/article/article.tex
First COINed draft sent to Stefan. Small things remain to be finished.

\documentclass[a4paper,doc,floatsintext,natbib]{apa6}%article}
% \documentclass{article}
\usepackage[font=small]{caption}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[utf8]{inputenc}
\usepackage{nameref}
\usepackage{todonotes}
\usepackage{authblk}
% \usepackage[nomarkers,figuresonly]{endfloat}
\usepackage{multirow}
\usepackage{tabularx}

@@

\section{Results}
Using the COIN model \citep{Heald_Contextual_2021}, we simulated representative experiments from a number of experimental studies on motor adaptation to illustrate how our model explains these experimental findings using the dynamics of context inference. We will present these simulations alongside the experimental results from the representative studies and discuss in detail how context inference explains the experimental phenomena.

@@

\begin{figure}
\centering
\includegraphics[]{./figures/figure_1.png}
\caption{Schematic representation of the model and simulations. (A) Generative model. Clear circles represent the observables, i.e. motor commands $u_t$ and direct observations $y_t$ (e.g. cursor position). The real context $\zeta_t$ is not directly observable, but influences $y_t$. The dark rectangles represent the prior distributions for the inferred adaptation level $x_t$ (Normal-Gamma distribution) and the current context $\zeta_t$ (discrete distribution with known $\pi$; see Methods). At every trial, the context is inferred, then motor adaptation is carried out and finally a motor command is issued; the flow of this process is indicated by the gray arrow in the background, while black arrows show the direction of information flow. (B) Simulations obtained with the model in (A), using an experimental setup similar to that by \cite{Davidson_Scaling_2004}. The plots are organized as follows: each pair of plots represent context inference (bottom; p(ctx)) and response/adaptation (top). In the context inference plot, the y-axis represents the posterior probability of each context $p(\zeta_t = j$; the black line represents the baseline context (i.e. no adaptation), the green line represents the only adaptation to be learned during the simulated experiment. In the top plot (adaptation), the y-axis is the adaptation to be learned (e.g. the angle in a visuomotor rotation experiment), using the same color scheme (black for baseline). The purple line is the agent's response for the trial. The shaded areas represent the standard deviation around the mean, obtained across 50 simulated participants. Note, however, that the top plots are shown for a single run, for clarity (see main text). A total of 3x3 experiments were simulated, with low, medium and high levels of both cue uncertainty and observation noise. All plots share the same x-axis, which represents the trial number.}
\label{fig:model}
\end{figure}
\todo{Probably remove the top plots, as they are hard to explain and add very little to the paper}
While these priors are not mathematically equivalent to those used by \cite{Heald_Contextual_2021}, the prior samples they produce can be shown to be similar. For more details, see the supplementary materials. \todo{Do this}

@@

The first column of \fref{fig:model} shows that, in the presence of reliable contextual cues, context inference is correct, certain and fast to switch. However, as contextual cues become less reliable, switching between known contexts becomes slower, as seen in the posterior probabilities over contexts at and after trial 20 in the second and third columns. Furthermore, as perceptual noise increases, switching becomes not only slower, but also more uncertain, with individual agents incorrectly missing the switch entirely.

@@

\subsection{Experimental results}
In this section, we present experimentally-observed phenomena in three sections, and show that the dynamics of context inference provide a unifying explanation for all of them. In the first section, we discuss switches between contexts, and how slow context inference affects these switches. In the second section, we focus on the effects of volatility in the environment on motor adaptation. Finally, in the third section we discuss context inference during so-called error-clamp trials, and its effect on behavior. For each of the three sections, we selected one or two studies which are representative of the phenomenon being discussed.

@@

\subsubsection{Savings and slow/fast switching}
The term 'savings' refer to the ability to remember a previously-learned adaptation and apply it without having to re-learn it. Savings is almost universally observed in humans \citep{Brashers-Krug_Consolidation_1996,Shadmehr_Functional_1997,Medina_Mechanism_2001,Smith_Interacting_2006,Zarahn_Explaining_2008}. In an O-A-O-A experiment, for example, savings would express themselves in the second A block in the form of a much higher adaptation rate higher than that observed during the first A block. The related concept of quick de-adaptation occurs in A-O transitions, where participants switch back to baseline without having to re-learn it.

@@

To show this, we examined multiple experimental studies in which savings are observed. We categorized these studies based on the amount of contextual information made available to participants: In some experiments \citep[e.g.][]{Kim_Neural_2015,Lee_Dual_2009}, the context is clearly revealed to the participant. We call these cued-context experiments. In other experiments, partial information is available to participants \citep[e.g.][]{Davidson_Scaling_2004,Zarahn_Explaining_2008} in the form of large prediction errors, partial contextual information or reward prediction errors; we refer to these as partially-cued experiments.

We selected three representative experiments from two studies \citep{Kim_Neural_2015,Oh_Minimizing_2019} which differ in the amount of contextual information available to participants. \cite{Kim_Neural_2015} performed a cued-context visuomotor rotation experiment with three contexts with different rotation: no rotation, 40 degrees and -40 degrees. Participants performed shooting movements in blocks of trials with the same rotation. Importantly, a colored light identified the current context, making this a cued-context experiment. Consistent with our model, the authors found that switching was immediate and accurate.

In \fref{fig:oh-2019}A we show the results of simulations with our model using the parameters of the task, as well as the experimental results from \cite{Kim_Neural_2015}. The correspondence between simulations and experimental results can be seen in the switches between contexts in the center panel, i.e. when the solid gray line (representing the true context) switches between 40, 0 and -40; in both panels (second and third), the thick black line, representing the agent's adaptation, quickly follows these switches.

@@

Critically, in \fref{fig:oh-2019}A it can be seen for the first four context switches (until about trial 250) that participants had not yet completely adapted to the rotation, as evidenced by their responses not being on par with the true rotation angle. This undershooting of responses (i.e. not doing the 40 degree rotation) happens despite participants being able to immediately and with high certainty identify the real context, as shown in the first-column panel. These results are similar to those shown by \cite{Imamizu_Explicit_2007}, where sensory cues of varying reliability effected immediate or slow contextual switches. To expand on these results, we now turn to feedback and its effects on switching behavior.

\cite{Oh_Minimizing_2019} performed two partially-cued experiments with a visual rotation of 20 and 10 degrees, respectively. The results of their experiments can be seen in \fref{fig:oh-2019}B and \ref{fig:oh-2019}C, alongside simulations with our model. Participants in the first experiment (\fref{fig:oh-2019}B) first learned the adaptation in $A$. In subsequent $A - O$ transitions, participants showed immediate switching (with a one-trial lag) between A and O (both ways), which can be seen in their responses (black line in the last two columns of \fref{fig:oh-2019}B) closely following the switches in the black line (true rotation). In the second experiment (\fref{fig:oh-2019}C), switching happens more slowly, with adaptation lagging behind the switches in the real context, and slowly catching up. As can be seen in the left panels in \fref{fig:oh-2019}B and \ref{fig:oh-2019}C, the same model parametrization produces fast, accurate switches when the adaptation is large (B), and slow, noisy switches when it is low (C). This difference is explained in our simulations in terms of the size of the adaptation in relation to observation noise: as the adaptation is smaller (10 degrees), it becomes more difficult to distinguish errors made by incorrectly inferring the context from the noise due to trial-to-trial variation in motor output. Because of this, the model requires more evidence (i.e. more trials) to infer a switch in contexts.

Note that the results from our simulations, from \cite{Oh_Minimizing_2019} and from \cite{Kim_Neural_2015} include both savings (O-A transitions) and de-adaptation (A-O transitions), both of which display the same characteristics and are explained by the same mechanism.

\subsubsection{Uncertainty over contexts affects action selection}
As with learning, action selection is affected by context inference. If the identity of the current context is known, the forward model for this context is used to select the current action. However, if uncertainty over the context exists, the selected action is influenced by all the possible contexts, with a weight directly related to how likely each one of those contexts is (see \eref{eqn:dist-comm}).

@@

We simulated data with our model fitting the experimental structure in \cite{Davidson_Scaling_2004}. We show the results in \fref{fig:davidson-2004}A, alongside the experimental results from \cite{Davidson_Scaling_2004}. It can be seen that the agent exposed to the -A context shifts back to A more slowly than the one exposed to 3A, qualitatively reproducing the data from \cite{Davidson_Scaling_2004}.

@@

To confirm our hypothesis, we simulated variants of the experiments in which the context-inference account predicts that the difference between groups disappears. First, in \fref{fig:davidson-2004}B, we simulated an experiment in which the contexts have more extreme adaptations, making them more different from baseline than in the \cite{Davidson_Scaling_2004} experiments. To do this, one group adapts in a $O-A-(-2A)$ paradigm, while the other group adapts in a $0-A-4A$ paradigm. As in the original experiment, the second contexts ($-2A$ for one group, $4A$ for the other) are equally spaced from the first context. However, given the larger distance from baseline, the baseline context has a much lower attribution when the switch occurs compared to the original experiment. This change makes both simulated groups infer the correct context in much more similar times, making the difference between their errors be much smaller compared to the original experiment. Furthermore, we simulated an experiment with an identical structure to that of \cite{Davidson_Scaling_2004}, but eliminated the baseline context from the agent. The results can be seen in \fref{fig:davidson-2004}C, where the switches between contexts are made identically by the two groups. We discuss possible implementations of such an experiment in the Discussion section, alongside with other predictions made by the model. \todo{Promises, promises}

@@

Because context inference integrates information from different sources, many experiments in which no intentional, overt contextual cues are available indeed contain contextual information that the participant can use to infer the context. For example, proprioceptive signals  provide contextual information \citep{Dizio_Motor_1995,Shadmehr_Adaptive_1994}. The sudden appearance of motor errors can itself be a cue for contextual change \citep{Herzfeld_memory_2014} and even a pause between two trials could suggest a change in context \cite{Ethier_Spontaneous_2008}.

@@

\cite{Vaswani_Decay_2013} studied in detail human behavior during an error-clamp block in a shooting movement paradigm with a mechanical arm. The authors found that during an E block at the end of each experiment, there was a lag of a few trials (depending on participant) before their motor behavior changed from that of the previous block. After that, the exerted force slowly dropped towards zero throughout tens of trials, but never reaching values around zero. Participants were divided into four groups, each of which going through a different block sequence: (1) A-E, (2) O-A-E, (3) (-A/2)-A-E, and (4) (-A)-E. No pauses were made during the experiment nor were there any contextual cues, so transitions between blocks were not signaled to participants.

In \fref{fig:vaswani-2013}A, we show data simulated with the COIN, following the parameters of the experiment by \cite{Vaswani_Decay_2013}, and in \fref{fig:vaswani-2013}B we show the experimental plots adapted from \cite{Vaswani_Decay_2013}. The displayed adaptation is shown during the E trials for the three experimental groups in the experiment. It can be seen that group 1.3 (i.e. the participants who had learned in the -A/2 context in addition to A) more quickly recognized a change in context and lowers the force applied on the mechanical handle, as can be seen in the experimental data.

@@

We selected representative experimental studies that show the well-established effects of savings, quick de-adaptation, spontaneous recovery and the effects of sensory cues. Using our model, we showed how each of these effects can be explained by the specifics of context inference, which integrates all the available information (e.g. sensory cues, workspace location, reward and endpoint feedback), in some cases throughout many trials.

@@

The same rationale explains the results by \cite{Herzfeld_memory_2014}: motor learning, which in our model is modulated by context inference, is minimal for errors close to 2 and -2 (see their figure 2E). This is because an error of 2 or -2 signals that the participant incorrectly identified the context (as adaptation has a magnitude of 1). Additionally, as was shown by \cite{Heald_Contextual_2021}, context inference explains the modulation of learning rate by the volatility of the environment observed by \cite{Herzfeld_memory_2014}.

@@

\subsubsection{Reducing the effect of volatility on learning}
Experiments \citep{Herzfeld_memory_2014} have shown an effect of the volatility of the environment (i.e. unpredictable switching between contexts) on measured learning rate. Our model predicts that this effect would be greatly reduced if reliable contextual cues were introduced: if a participant can infer the context of the current trial before any decision or observation has occurred, the learning rate would not be affected by the volatility of the environment. \cite{Heald_Contextual_2021} showed that the COIN model explains this change in terms of the Kalman gain and the posterior probability over contexts (see their equation 14) \todo{Check this in more detail}.

If this prediction is confirmed, our model would additionally suggest that human participants do not revisit the learned adaptation of the previous trial when a new observation comes in. To see this, consider the following scenario from the experiments by \cite{Herzfeld_memory_2014}: at trial $t$, the true context was B but the participant inferred context A, issued a motor command consistent with context A and then observed the outcome at $t + 1$. When the outcome is observed, it becomes clear to the participant that the context was B. Does the participant update the internal model of A or of B? According to our model, participants incorrectly update A and, upon learning of their mistake at trial $t+1$, do not revert this update. If this were not the case, the volatility of the environment would have no effect even without contextual cues, as the context at trial $t$ can almost always be identified at trial $t+1$.

@@

Action selection (i.e. motor output $u_t$) is done via the weighted mean of $x_{j,t}$:
\begin{equation}
u_t  = \displaystyle\sum_{j}p(\zeta_{j,t} | ...) x_{j,t}
\end{equation}
To include motor noise (independent from estimation uncertainty), as well as carry over the uncertainty over $x_{j,t}$, we instead sample motor commands from a Gaussian centered on this mean, with a standard deviation $\sigma_u$, which is a free parameter of the model.

>>>>

\documentclass[a4paper,doc,floatsintext,natbib]{apa6}
%% \documentclass{article}
\usepackage[font=large]{caption}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[utf8]{inputenc}
\usepackage{nameref}
\usepackage{todonotes}
\usepackage{authblk}
% \usepackage[nomarkers,figuresonly]{endfloat}
\usepackage{multirow}
\usepackage{tabularx}

@@

\section{Results}
Using the COIN model \citep{Heald_Contextual_2021}, we simulated representative experiments from a number of experimental studies on motor adaptation to illustrate how this model explains these experimental findings using the dynamics of context inference. We will present these simulations alongside the experimental results from the representative studies and discuss in detail how context inference explains the experimental phenomena.

@@

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{./figures/figure_1.png}
\caption{Schematic representation of the model and simulations. (A) Generative model. Clear circles represent the observables, i.e. motor commands $u_t$ and direct observations $y_t$ (e.g. cursor position). The real context $\zeta_t$ is not directly observable, but influences $y_t$. The dark rectangles represent the prior distributions for the inferred adaptation level $x_t$ (Normal-Gamma distribution) and the current context $\zeta_t$ (discrete distribution with known $\pi$; see Methods). At every trial, the context is inferred, then motor adaptation is carried out and finally a motor command is issued; the flow of this process is indicated by the gray arrow in the background, while black arrows show the direction of information flow. (B) Simulations obtained with the model in (A), using an experimental setup similar to that by \cite{Davidson_Scaling_2004}. The plots are organized as follows: each pair of plots represent context inference (bottom; p(ctx)) and response/adaptation (top). In the context inference plot, the y-axis represents the posterior probability of each context $p(\zeta_t = j$; the black line represents the baseline context (i.e. no adaptation), the green line represents the only adaptation to be learned during the simulated experiment. In the top plot (adaptation), the y-axis is the adaptation to be learned (e.g. the angle in a visuomotor rotation experiment), using the same color scheme (black for baseline). The purple line is the agent's response for the trial. The shaded areas represent the standard deviation around the mean, obtained across 50 simulated participants. Note, however, that the top plots are shown for a single run, for clarity (see main text). A total of 3x3 experiments were simulated, with low, medium and high levels of both cue uncertainty and observation noise. All plots share the same x-axis, which represents the trial number.}
\label{fig:model}
\end{figure}
\todo{Probably remove the top plots, as they are hard to explain and add very little to the paper}
These priors are not mathematically equivalent to those used by \cite{Heald_Contextual_2021}, but the prior samples they produce can be shown to be similar. For more details, see the supplementary materials. \todo{Do this}.

@@

The first column of \fref{fig:model} shows that, in the presence of reliable contextual cues, context inference is accurate, certain and fast to switch. However, as contextual cues become less reliable, switching between known contexts becomes slower, as seen in the posterior probabilities over contexts at and after trial 20 in the second and third columns. Furthermore, as perceptual noise increases, switching becomes not only slower, but also more uncertain, with individual agents incorrectly missing the switch entirely.

@@

\subsection{Experimental results}
In this section, we present experimentally-observed phenomena in three sections, and show that the dynamics of context inference provide a unifying explanation for all of them. In the first section, we discuss switches between contexts, and how slow context inference affects these switches. In the second section, we focus on interference between learned adaptations. Finally, in the third section we discuss context inference during error-clamp trials, and its effect on behavior. For each of the three sections, we selected one or two studies which are representative of the phenomenon being discussed.

@@

\subsubsection{Savings and slow/fast switching}
The term 'savings' refer to the ability to remember a previously-learned adaptation and apply it without having to re-learn it. Savings is almost universally observed in humans \citep{Brashers-Krug_Consolidation_1996,Shadmehr_Functional_1997,Medina_Mechanism_2001,Smith_Interacting_2006,Zarahn_Explaining_2008}. In an O-A-O-A experiment, for example, savings would express themselves in the second A block in the form of a much higher adaptation rate than that observed during the first A block. The related concept of quick de-adaptation occurs in A-O transitions, where participants switch back to baseline without having to re-learn it.

@@

To show this, we examined multiple experimental studies in which savings are observed. We categorized these studies based on the amount of contextual information made available to participants: In some experiments \citep[e.g.][]{Kim_Neural_2015,Lee_Dual_2009}, the context is clearly revealed to the participant using sensory cues. We call these cued-context experiments. In other experiments, partial information is available to participants \citep[e.g.][]{Davidson_Scaling_2004,Zarahn_Explaining_2008} in the form of large prediction errors, partial contextual information or reward prediction errors; we refer to these as partially-cued experiments.

We selected three representative experiments from two studies \citep{Kim_Neural_2015,Oh_Minimizing_2019} which differ in the amount of contextual information available to participants. \cite{Kim_Neural_2015} performed a cued-context visuomotor rotation experiment with three contexts with different rotation: no rotation, 40 degrees and -40 degrees. Participants performed shooting movements in blocks of trials with the same rotation. Importantly, a colored light identified the current context, making this a cued-context experiment. Consistent with the context-inference account, the authors found that switching was immediate and accurate.

In \fref{fig:oh-2019}A we show the results of simulations with the model using the parameters of the task, as well as the experimental results from \cite{Kim_Neural_2015}. The correspondence between simulations and experimental results can be seen in the switches between contexts in the center panel, i.e. when the solid gray line (representing the true context) switches between 40, 0 and -40; in both panels (second and third), the thick black line, representing the agent's adaptation, quickly follows these switches.

@@

Critically, in \fref{fig:oh-2019}A it can be seen for the first four context switches (until about trial 250) that participants had not yet completely adapted to the rotation, as evidenced by their responses not being on par with the true rotation angle. This undershooting of responses (i.e. not doing the 40 degree rotation) happens despite participants being able to immediately and with high certainty identify the real context, as shown in the first-column panel. These results are similar to those shown by \cite{Imamizu_Explicit_2007}, where sensory cues of varying reliability effected immediate or slow contextual switches.

To expand on these results, we now turn to feedback and its effects on switching behavior. \cite{Oh_Minimizing_2019} performed two partially-cued experiments with a visual rotation of 20 and 10 degrees, respectively. The results of their experiments can be seen in \fref{fig:oh-2019}B and \ref{fig:oh-2019}C, alongside simulations with the COIN model. Participants in the first experiment (\fref{fig:oh-2019}B) first learned the adaptation in $A$. In subsequent $A - O$ transitions, participants showed immediate switching (with a one-trial lag) between A and O (both ways), which can be seen in their responses (black line in the last two columns of \fref{fig:oh-2019}B) closely following the switches in the black line (true rotation). In the second experiment (\fref{fig:oh-2019}C), switching happens more slowly, with adaptation lagging behind the switches in the real context, and slowly catching up. As can be seen in the left panels in \fref{fig:oh-2019}B and \ref{fig:oh-2019}C, the same model parametrization produces fast, accurate switches when the adaptation is large (B), and slow, noisy switches when it is low (C). This difference is explained in our simulations in terms of the size of the adaptation in relation to observation noise: as the adaptation is smaller (10 degrees), it becomes more difficult to distinguish errors made by incorrectly inferring the context from the noise due to trial-to-trial variation in motor output. Because of this, the model requires more evidence (i.e. more trials) to infer a switch in contexts.

Note that the results from our simulations from \cite{Oh_Minimizing_2019} and from \cite{Kim_Neural_2015} include both savings (O-A transitions) and de-adaptation (A-O transitions), both of which display the same characteristics and are explained by the same mechanism.

\subsubsection{Uncertainty over contexts affects action selection}
As with learning, action selection  affected by context inference. If the identity of the current context is known, the forward model for this context is used to select the current action. However, if uncertainty over the context exists, the selected action is influenced by all the possible contexts, with a weight directly related to how likely each one of those contexts is (see \eref{eqn:dist-comm}).

@@

We simulated data with the model fitting the experimental structure in \cite{Davidson_Scaling_2004}. We show the results in \fref{fig:davidson-2004}A, alongside the experimental results from \cite{Davidson_Scaling_2004}. It can be seen that the agent exposed to the -A context shifts back to A more slowly than the one exposed to 3A, qualitatively reproducing the data from \cite{Davidson_Scaling_2004}.

@@

To confirm our hypothesis, we simulated variants of the experiments in which the context-inference account predicts that the difference between groups disappears. First, in \fref{fig:davidson-2004}B, we simulated an experiment in which the contexts have more extreme adaptations, making them more different from baseline than in the \cite{Davidson_Scaling_2004} experiments. To do this, one group adapts in a $O-A-(-2A)$ paradigm, while the other group adapts in a $0-A-4A$ paradigm. As in the original experiment, the second contexts ($-2A$ for one group, $4A$ for the other) are equally spaced from the first context. However, given the larger distance from baseline, the baseline context has a much lower attribution when the switch occurs compared to the original experiment. This change makes both simulated groups infer the correct context almost equally quickly, making the difference between their errors be much smaller compared to the original experiment. Furthermore, we simulated an experiment with an identical structure to that of \cite{Davidson_Scaling_2004}, but eliminated the baseline context from the agent. The results can be seen in \fref{fig:davidson-2004}C, where the switches between contexts are made identically by the two groups. We discuss possible implementations of such an experiment in the Discussion section, alongside with other predictions made by the model. \todo{Promises, promises}

@@

@@

\cite{Vaswani_Decay_2013} studied in detail human behavior during an error-clamp block in a shooting movement paradigm with a mechanical arm. The authors found that during an E block at the end of each experiment, there was a lag of a few trials (depending on participant) before their motor behavior changed from that of the previous block. After that, the exerted force slowly dropped towards zero throughout tens of trials, but never reaching values around zero. Participants were divided into four groups, each of which going through a different block sequence: (1) A-E, (2) O-A-E, (3) (-A/2)-A-E, and (4) (-A)-E. No pauses were made during the experiment nor were there any contextual cues, so transitions between blocks were not signaled to participants. However, because context inference integrates information from different sources, many experiments in which no intentional, overt contextual cues are available indeed contain contextual information that the participant can use to infer the context. For example, proprioceptive signals  provide contextual information \citep{Dizio_Motor_1995,Shadmehr_Adaptive_1994}. The sudden appearance of motor errors can itself be a cue for contextual change \citep{Herzfeld_memory_2014} and even a pause between two trials could suggest a change in context \citep{Ethier_Spontaneous_2008}.

In \fref{fig:vaswani-2013}A, we show data simulated with the COIN model, following the parameters of the experiment by \cite{Vaswani_Decay_2013}, and in \fref{fig:vaswani-2013}B we show the experimental plots adapted from \cite{Vaswani_Decay_2013}. The displayed adaptation is shown during the E trials for the three experimental groups in the experiment. It can be seen that group 1.3 (i.e. the participants who had learned in the -A/2 context in addition to A) more quickly recognized a change in context and lowers the force applied on the mechanical handle, as can be seen in the experimental data.

@@

We selected representative experimental studies that show the well-established effects of savings, quick de-adaptation, spontaneous recovery and the effects of sensory cues. Using the COIN model introduced by \cite{Heald_Contextual_2021}, we showed how each of these effects can be explained by the dynamics of context inference, which integrates all the available information (e.g. sensory cues, workspace location, reward and endpoint feedback), in some cases throughout many trials.

@@

The same rationale explains the results by \cite{Herzfeld_memory_2014}: motor learning, which in the COIN model is modulated by context inference, is minimal for errors close to 2 and -2 (see their figure 2E). This is because an error of 2 or -2 signals that the participant incorrectly identified the context (as adaptation has a magnitude of 1). Additionally, as was shown by \cite{Heald_Contextual_2021}, context inference explains the modulation of learning rate by the volatility of the environment observed by \cite{Herzfeld_memory_2014}.

@@

\subsubsection{Interference effects}
As discussed in the Resuls section, the effect observed by \cite{Davidson_Scaling_2004} is explained by the model as an effect of slow context inference, instead of being a direct interference at the level of learning. As shown in \fref{fig:davidson-2004}B-C, the context inference account predicts that this effect would disappear if all contexts were significantly different from baseline, such that the baseline context never explains the observations. Removing the baseline context from a participant's context inference might be experimentally unfeasible, but other possibilities include making all adaptations bigger (e.g. bigger angles, stronger forces), and including contextual cues that rule out the baseline context. In the opposite direction, the model predicts that if all adaptations are smaller (i.e. closer to baseline), the differences between the two groups would increase.

\subsubsection{Reducing the effect of volatility on learning}
Experiments \citep{Herzfeld_memory_2014,Heald_Contextual_2021} have shown an effect of the volatility of the environment (i.e. unpredictable switching between contexts) on measured learning rate. The model predicts that this effect would be greatly reduced if reliable contextual cues were introduced: if a participant can infer the context of the current trial before any decision or observation has occurred, the learning rate would not be affected by the volatility of the environment. \cite{Heald_Contextual_2021} showed that the COIN model explains this change in terms of the Kalman gain and the posterior probability over contexts (see their equation 14) \todo{Check this in more detail}.

If this prediction is confirmed, the model would additionally suggest that human participants do not revisit the learned adaptation of the previous trial when a new observation comes in. To see this, consider the following scenario from the experiments by \cite{Herzfeld_memory_2014}: at trial $t$, the true context was B but the participant inferred context A, issued a motor command consistent with context A and then observed the outcome at $t + 1$. When the outcome is observed, it becomes clear to the participant that the context was B. Does the participant update the internal model of A or of B? According to the model, participants incorrectly update A and, upon learning of their mistake at trial $t+1$, do not revert this update. If this were not the case, the volatility of the environment would have no effect even without contextual cues, as the context at trial $t$ can almost always be identified at trial $t+1$.

@@

Action selection (i.e. motor output $u_t$) is done via the weighted mean of $x_{j,t}$:
\begin{equation}
u_t  = \displaystyle\sum_{j}p(\zeta_{j,t} | ...) x_{j,t} \label{eqn:dist-comm}
\end{equation}
To include motor noise (independent from estimation uncertainty), as well as carry over the uncertainty over $x_{j,t}$, we instead sample motor commands from a Gaussian centered on this mean, with a standard deviation $\sigma_u$, which is a free parameter of the model.
